Human tissue specific markers

### 2017-06-08 manuscript/manuscript.Rnw
use cref instead of fref
make figures 4x4

\begin{figure}
<<uterus.specific.markers.figure,fig.width=8,fig.height=8,echo=FALSE>>=
print(specific.markers.plot("uterus")
      + xlab("Genes Characteristic of Uterus ")
      + ylab("Tissue"))
@
\caption{Expression of genes characteristic of uterus
  ($\tau_g \ge 0.98$) in uterus and all tissues with the second
  highest expression for any of the uterus-characterizing genes
  ordered by their tissue specificity. The known uterus-characterizing
  gene PAEP and short RNAs ZNFX1-AS1\_3 (87bp) and AL356310.1 (94bp)
  are highly characteristic of uterus.}
\label{fig:uterus_specific_markers}
\end{figure}

@@

This occured because the placenta FPKMs we based the original list on
did not properly align against miRNA or snRNA
\fref{tab:missing_uterus_specific_genes}. The uterus calls also appear
to be wrong or cooked; for example, SNORD5 has counts of 7000ish which
are not inside of its confidence interval. This may be indicative of a
off-by-one error or something else that is screwed up in their file.

@@

\begin{figure}
<<placenta.specific.markers.figure,fig.width=8,fig.height=8,echo=FALSE>>=
print(specific.markers.plot("placenta",
                            genes=as.character(tissue.specific.genes[tissue=="placenta" & 
                                                                         gi.max >= 1024
                               ,gene]))
      + xlab("Genes Characteristic of Placenta")
      + ylab("Tissue"))
@

@@

\begin{figure}
<<placenta.roc.curve,fig.width=8,fig.height=8,echo=FALSE>>=
layout(matrix(c(1,3,2,4),2,2))
pl.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"placenta"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#002058"
             )
pl.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"placenta"]),
              percent=TRUE,
              col="#E87722")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))

>>>>

\begin{figure}
<<uterus.specific.markers.figure,fig.width=4,fig.height=4,echo=FALSE>>=
print(specific.markers.plot("uterus")
      + xlab("Genes Characteristic of Uterus ")
      + ylab("Tissue"))
@
\caption{Expression of genes characteristic of uterus
  ($\tau_g \ge 0.98$) in uterus and all tissues with the second
  highest expression for any of the uterus-characterizing genes
  ordered by their tissue specificity. The known uterus-characterizing
  gene PAEP and short RNAs ZNFX1-AS1\_3 (87bp) and AL356310.1 (94bp)
  are highly characteristic of uterus.}
\label{fig:uterus_specific_markers}
\end{figure}

@@

This occured because the placenta FPKMs we based the original list on
did not properly align against miRNA or snRNA
\cref{tab:missing_uterus_specific_genes}. The uterus calls also appear
to be wrong or cooked; for example, SNORD5 has counts of 7000ish which
are not inside of its confidence interval. This may be indicative of a
off-by-one error or something else that is screwed up in their file.

@@

\begin{figure}
<<placenta.specific.markers.figure,fig.width=4,fig.height=4,echo=FALSE>>=
print(specific.markers.plot("placenta",
                            genes=as.character(tissue.specific.genes[tissue=="placenta" & 
                                                                         gi.max >= 1024
                               ,gene]))
      + xlab("Genes Characteristic of Placenta")
      + ylab("Tissue"))
@

@@

\begin{figure}
<<placenta.roc.curve,fig.width=4,fig.height=4,echo=FALSE>>=
layout(matrix(c(1,3,2,4),2,2))
pl.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"placenta"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#002058"
             )
pl.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"placenta"]),
              percent=TRUE,
              col="#E87722")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))
